\documentclass[letterpaper,9.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/ashishrana160796/}{\Large Ashish Rana}} & Email : \href{mailto:ashishrana160796@gmail.com}{ashishrana160796@gmail.com}\\
  \href{https://ashishrana160796.github.io/}{ashishrana160796.github.io} & Mobile : +91-94573-95571 \\
  \href{https://linkedin.com/in/ashishrana160796/}{LinkedIn : linkedin.com/in/ashishrana160796} & \href{http://github.com/ashishrana160796/}{Github : github.com/ashishrana160796} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {American Express}{\textit{Next Generation Data Management Team, Bengaluru}}
      {Data Engineering Intern}{Jan 2019 - Present}
      \resumeItemListStart
        \resumeItem{Automation, Data pipeline and Administrative Scripts }
          {For monitoring stats of Couchbase VMs, multiprocessing VM patching and automating post provisioning steps. Reducing resource comsumption upto 50 to 90 \% for multiple tasks.}
        \resumeItem{Researching Next Generation Cloud Databases}
          {Benchmarking their results \& architecture analysis with current existing industrial datastores.}
        \resumeItem{Research \& Development of Database Monitoring Tools*}
          {Graphana \& Splunk visualization with Elasticsearch \& Prometheus datastores with Python, Ansible \& Golang scripts.}
        \resumeItem{Extra Initiatives}
          {Built a clustering based recommendation system and In-house human technical resource helper tool by scraping Confluence pages for CIO's presentation. Working with multi-disciplinary teams and developing business use-case understanding. Planned and organized intern outings, birthdays \& farewells. }
      \resumeItemListEnd
      

    \resumeSubheading
      {GE}{\textit{Product Lifecycle Management COE Team, Bengaluru}}
      {Software Engineering Intern}{Jun 2018 - July 2018}
      \resumeItemListStart
        \resumeItem{ReST Web-Services}
          {Implemented ReST web-services from legacy SOAP with microservices compatible concept.}
        \resumeItem{SSO SAML Authentication}
          {Resolved logout and reauthentication issues, increased the use case coverage.}
        \resumeItem{Static Tool Analysis}
          {POC case study w/ multiple tools and Enterprise scale solutions designed, github contributions to original tools.}
        \resumeItem{UI Enchancements}
          {Dialog box help designed and implemented with custom library compatible code, reduces user effort.}
        \resumeItem{Functional Learnings}
          {Business understanding for application user base of 40,000, international team meetings, presented curriculum and solutions with extensive documentation, gap analysis, stretch assignments initiative.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Recent Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{Global Rank: 210, October Mega Cook-Off 2018}
      {achieved on Codechef coding platform for username rana\textunderscore160796.}
    \resumeSubItem{Author,  TowardsDataScience \& AnalyticsVidhya}
      {Published several articles on Deep Learning, ML, AI and Reinforcement learning with 38K+  views and 225+ unique recommendations.}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Clustering Based Online Recommendation System}
      {Based on course data from Pluralsight a clustering and LDA based recommendation system that uses elbow method for finding approximate number of cluster to minimize SSE.}
    \resumeSubItem{CheckerFramework, Contributor}
      {2500+ lines of code committed, for jdk annotations. Created prototype type system for determinism in code. Minor contributions, other tools and case study done for Enterprise applications.}
    \resumeSubItem{Optimization Algorithm GUI}
      {Convergence calculations for multidimensional fitness functions. Algorithms available like DE, GA, PSO, Random Walk. Extra comparative	python implementation for efficiency comparison.}

    \resumeSubItem{Aimacode, Contributor}
      {Contributing AI pseudocode algorithms. Specification Issues raised for aima/java.}
    \resumeSubItem{Markov Chain Music Generator}
      {Music generation of Indian classical music with finite visible markov chains with \textit{mido}.}
    \resumeSubItem{Deep Vision Tool: Final Year Project}
      { 
        Deep learning deployment solutions with Desktop based GUI and custom E-mail based replies for VQA based object classification \& Activity Classfication module.
	    \resumeItemListStart
        \resumeItem{Chatbot Module}
          {NLP query helper Chatbot with LSSVM based intent detection decision flows and encoded personality.}
       \resumeItemListEnd
      }
          \resumeSubItem{TreasureHunt App}
      {Zbar library for QR code scanning used. With puzzle editability and test concurrency for 400 users.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java}{(\textit{Proficient})}{,}{ Python}{(\textit{Proficient})}{,}{ Ansible}{,}{ R}{,}{ Shell}{ Scripting}{,}{ C}{,}{ C++}{,}{ SQL}{,}{ PL/SQL}{,}{ JS}{,}{ jQuery}{,}{ MatLab}{,}{ UML}{,}{ ARM}{,}{ Verilog}{,}{ 8085}{,}{ 8086}{,}{ Arduino}
      \textbf{, Technologies: }{ Scikit-learn}{,}{ Tensorflow}{,}{PyTorch}{,}{ NetworkX}{,}{ nltk}{,}{ Tkinter}{,}{ Git}{,}{ Linux}{,}{ Static Analysis Tools}{,}{ SAML}{,}{ SiteMinder}{,}{ Jekyll}{,}{ Adobe Suite}{,}{ Microsoft Suite}
    }
  \resumeSubHeadingListEnd

%--------COURSES------------
\section{Courses}
  \resumeSubHeadingListStart
    \item{
      
      \textbf{Elective:}{ Deep Learning}{,}{ AI Search Methods}{,}{ ML}{,}{ NLP}{,}{ Data Analytics}{,}{ Data Mining}{,}{ Social Networks}{,}{ Cloud Computing}
      \textbf{, Core:}{ Image Processing}{,}{ Advanced Data Structure And Algorithms}{,}{ Software Engineering}{,}{ Information Management}{,}{ Numerical Analysis}{,}{ Optimizations}{,}{ Discrete Mathematics}{,}{ Networking}{,}{ OS}{,}{ TOC}{,}{ Compilers}{,}{ Computer Architecture}{,}{ Microprocessors}{,}{ Embedded Systems}
         }
  \resumeSubHeadingListEnd

%--------COURSES------------
\section{Co-curriculars}
  \resumeSubHeadingListStart
    \item{
      \textbf{OWASP: Design Head, }{produced sophisticated and professional designs with Photoshop suite.}
         }
    \item{
      \textbf{MARS(\textit{Robotics Society}): Core Team, }{Conducting workshops on maze-solvers, Arduino and advanced C++.}
         }
    \item{
      \textbf{Scimatics: Mentor, Design Head }{Conducting workshops on Java, C++, Arduino, graphic design. Mentoring juniors and Event management.}
         }
    \item{
      \textbf{Voluntary Experience: }{Destitute homes and Orphanage visits, Blood donor and Charity participation in college.}
         }         
\item{
      \textbf{Academics: }{Gold Medalist: Social Network(\textit{NPTEL-Course}), Gold Medalist: First Year(\textit{Branch}), Gold Medalist: School IMO}
         }         

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thapar Institute of Engineering and Technology}{Patiala, Punjab}
      {Computer Engineering, \textbf{CGPA: 9.45}}{2015 -- Present}
    \resumeSubheading
      {Army Public School}{Meerut Cantt, U.P : Jalandhar Cantt, Punjab}
      {12th,  \textbf{Percent: 91.00} : 10th,  \textbf{Percent: 93.10}}{2013 -- 2014 : 2011 -- 2012}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
