%% Note: For adding or deleting any work experience section

%% Added a gap year section for this section in order to specify gap in education.
%% This study gap specification is important in many masters curriculum's as a requirement. It's always better to be honest about it straight forward.
%% Delete the \iffalse and \fi tags to add this gap year section to the CV.


\sectionTitle{Profession Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Present} {Data Engineering Specialist | Data and Analytics Team}{GE Healthcare}{Bengaluru}
    {August 2019}    {
                      \begin{itemize}
                        
                        \item{Designed \& developed incremental log data analysis pipeline with AWS Glue jobs, PySpark data transformations with Zeppelin \& Elasticsearch datastore.}
                        \item{Designed \& developed ingestion and predictive outlier detection pipeline MR modality from multiple sensor data sources.}
                        \item {Worked on Weibull Regression for hazard estimation in \textit{R} for modality failure rate prediction assisting predictive maintenance.}
                        \item {Designed, developed and deployed terabyte scale ingestion procedures in \textit{PL/pgSQL} on AWS Redshift multiple modalities and across all regions.}
                        \item {Two times Impact Award \& one time Collaboration award recipient. Second runner-ups in football \& volleyball in all GE businesses.}
                      \end{itemize}
                    }
                    {Python, R, PL/pgSQL, AWS Redshift, Elasticsearch, Other AWS Services}
  \emptySeparator
  
  %% Added the gap year section for reference.
  %% Uncomment the below tags and start working with the gap section addition.
  \iffalse
  \experience
    {August 2014} {Study Year Gap | Multiple Competitive Exam Preparation}{XXX Test Cleared}{Bengaluru}
    {August 2013}    {
                      \begin{itemize}
                        
                        \item{Gave X exam score Y result. Present in top X\% of students.}
                        \item{Gave X exam score Y result. Present in top X\% of students.}
                      \end{itemize}
                    }
                    {Advanced Calculus, Differential Equations, Linear Algebra, General Knowledge}
  \emptySeparator
  \fi
  %% Added the gap year section for reference.
  
  \experience
    {June 2019} {Data Engineering Intern | Next Gen Data Management Team}{American Express}{Bengaluru}
    {January 2019}    {
                      \begin{itemize}
                        \item Developed Prometheus and Grafana based monitoring and alerting orchestrated tool from scratch for monitoring 1000+ Couchbase database VMs.
                        \item Designed, developed and deployed Couchbase VM metrics. Also, developed parallel VM patching script that reduces downtime by 4 times.
                        \item Benchmarked performance of Redis and RedisGraph databases with the existing stack. Also, received certification in Redis basics and RediSearch.
                        \item As extra initiative, developed Confluence page scrapper with ReST queries for content summarization. 
                        \item Planned and organized intern outings, birthdays \& farewells during the internship.
                      \end{itemize}
                    }
                    {Couchbase, Python, Grafana, Redis, Prometheus, ReST}
  \emptySeparator
  
  \experience
    {July 2018} {Software Engineering Intern | Product Lifecycle Management Team}{GE Digital}{Bengaluru}
    {Jun 2018}    {
                      \begin{itemize}
                        \item Added SAML re-authentication module in custome Enovia PLM code base as per FDA CRF 21 guidelines.
                        \item Implemented ReST based architecture from the existing SOAP legacy code.
                        \item Conducted and presented in-depth case study of open-source static analysis tools on Enovia Java codebase. Also, proposed centralized custom rule creation based solution with SonarLint and SonarQube tools.
                      \end{itemize}
                    }
                    {ReST, Static Code Analysis Tools, SAML, Java, JSPs}
  \emptySeparator
  
\end{experiences}
